A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-05-02 paper.tex
Added AbySynthe & Simple BDD Solver benchmarks from cluster

        %Plots
        \draw plot[mark=x, mark options={fill=white}] file {bench_termite.dat};
        \draw plot[mark=+, mark options={fill=white}] file {bench_demiurge.dat};
        \draw plot[mark=triangle, mark options={fill=white}] file {bench_simple.dat};

        \begin{scope}[shift={(30,20)}] 
            \draw (0,0) -- 
                plot[mark=x, mark options={fill=white}] (0.25,0) -- (0.5,0) 
                node[right]{Unbounded synthesis};
            \draw[yshift=\baselineskip] (0,0) -- 
                plot[mark=+, mark options={fill=white}] (0.25,0) -- (0.5,0)
                node[right]{Demiurge};
            \draw[yshift=2\baselineskip] (0,0) -- 
                plot[mark=triangle, mark options={fill=white}] (0.25,0) -- (0.5,0)
                node[right]{Simple BDD Solver 2};
        \end{scope}

>>>>

        %Plots
        \draw plot[mark=o, mark size=1pt, mark options={fill=white,color=red}] file {bench_termite.dat};
        \draw plot[mark=+, mark options={fill=white,color=blue}] file {bench_demiurge.dat};
        \draw plot[mark=triangle, mark options={fill=white}] file {bench_simple2.dat};
        \draw plot[mark=x, mark options={fill=white,color=green}] file {bench_abs1.dat};
%%%        \draw plot[mark=x, mark options={fill=white,color=green}] file {bench_abs2.dat};
%%%        \draw plot[mark=x, mark options={fill=white,color=green}] file {bench_abs3.dat};

        \begin{scope}[shift={(30,20)}] 
            \draw (0,0) -- 
                plot[mark=o, mark size=1pt, mark options={fill=white,color=red}] (0.25,0) -- (0.5,0) 
                node[right]{Unbounded synthesis};
            \draw[yshift=\baselineskip] (0,0) -- 
                plot[mark=x, mark options={fill=white,color=green}] (0.25,0) -- (0.5,0)
                node[right]{AbsSynthe (seq2)};
            \draw[yshift=2\baselineskip] (0,0) -- 
                plot[mark=+, mark options={fill=white,color=blue}] (0.25,0) -- (0.5,0)
                node[right]{Demiurge};
            \draw[yshift=3\baselineskip] (0,0) -- 
                plot[mark=triangle, mark options={fill=white}] (0.25,0) -- (0.5,0)
                node[right]{Simple BDD Solver 2};
        \end{scope}
